---
title: "splash_eye_quality_analysis"
author: "Jojo Hu"
date: "7/26/2022"
output: html_document
---

# Get Frame Rate
```{python, eval = F}
python3 /Users/jojohu/Documents/Splash/beh_analysis/eye_quality/get_frame_rate.py /Volumes/data/projects/smile/recordings/eye_recordings/splash/
```

# Get Eye Tracking Coding Results
```{r}
library(dplyr)
library(stringr)

eyeQ <-
  list.files(path = "/Volumes/data/projects/smile/recordings/eye_recordings/splash/results",
             pattern = ".csv$", full.names = T, recursive = T)

eyeQ <- eyeQ[-which(eyeQ %in% c("/Volumes/data/projects/smile/recordings/eye_recordings/splash/results/frame_rate.csv",
                                "/Volumes/data/projects/smile/recordings/eye_recordings/splash/results/skipped_frame.csv",
                                "/Volumes/data/projects/smile/recordings/eye_recordings/splash/results/time_stamp.csv",
                                "/Volumes/data/projects/smile/recordings/eye_recordings/splash/results/Data Quality Master Spreadsheet  - TD.csv",
                                "/Volumes/data/projects/smile/recordings/eye_recordings/splash/results/Data Quality Master Spreadsheet  - ASD.csv"))]

readEye <- function(file) {
  temp <- read.csv(file, stringsAsFactors = F)
  temp$File <- as.character(temp$File)
  
  temp <- 
    temp %>%
    mutate_if(is.logical, as.character)
  
  temp <- 
    temp %>%
    mutate_if(is.numeric, as.character)
  
  return(temp)
}

eyeQDDF <- lapply(eyeQ, readEye)

eyeQD <- do.call(bind_rows, eyeQDDF)
```

# Filter out frames that are not relevant to stimuli
```{r}
eyeQD <- 
  eyeQD %>%
  filter(Coder != "JH") %>%
  filter(!str_detect(LookCode, "Left|Right|Center|Away|Blink|Shifting|cannot_tell|Cannot_tell")) %>%
  filter(!LookCode %in% c("center", "left", "right", "away")) %>%
  distinct(.) %>%
  dplyr::select(-one_of("FrameRate")) %>%
  mutate(Frame = as.numeric(as.character(Frame))) %>%
  arrange(File, Frame) %>%
  dplyr::select(-one_of("frame_rate", "start_time", "start_frame", "end_time", "end_frame"))

unique(eyeQD$LookCode)

eyeQD$part_id <- str_extract(eyeQD$File, "smile_\\S{1}_\\S{3}")

eyeQD <-
  eyeQD %>%
  mutate(block = str_extract(File, "(?<=block_).*(?=_)"),
         block_zoom = str_extract(File, "(?<=block)[:digit:]"),
         trial = str_extract(File, "(?<=_[:digit:]_)\\S+$"),
         trial_zoom = str_extract(File, "(?<=block[[:digit:]]_)[:alpha:]*"),
         trial_number = str_extract(File, "\\S+(?=.smile)"),
         trial_number_zoom = str_extract(File, "[:digit:]$")) %>%
  mutate(trial_zoom = dplyr::recode(trial_zoom, star = "blockIntro"),
         File = basename(File))
```


```{r}
time_stamp <- read.csv("/Volumes/data/projects/smile/recordings/eye_recordings/splash/results/time_stamp.csv")  

eyeQD <- merge(eyeQD, time_stamp, by.x = "File", by.y = "File", all.x = T)

org_eyeQD <- eyeQD

# eyeQD <- org_eyeQD
```


```{r}
library(dplyr)

max_frame <-
  eyeQD %>%
  arrange(File, Frame) %>% 
  group_by(File) %>%
  top_n(1, Frame) %>%
  dplyr::select(File, Frame) %>%
  dplyr::rename("max_frame" = "Frame") %>%
  distinct(.)

min_frame <-
  eyeQD %>%
  arrange(File, Frame) %>% 
  group_by(File) %>%
  top_n(-1, Frame) %>%
  dplyr::select(File, Frame) %>%
  dplyr::rename("min_frame" = "Frame") %>%
  distinct(.)

eyeQD <- merge(eyeQD, max_frame, all.x = T)

eyeQD <- 
  eyeQD %>%
  group_by(File) %>%
  filter(max_frame < 4800) %>%
  filter(max_frame > 10)
```


```{r}
# To Do: To make sure things are absolutely correct, manually mark actual start and end frames
# Filter only the frames with stimuli display
eyeQD_timed <-
  eyeQD %>%
  arrange(File, Frame) %>%
  group_by(File) %>%
  filter(!is.na(start_frame)) %>%
  filter(!is.na(end_frame)) %>%
  filter(Frame > start_frame & Frame < end_frame) %>%
  dplyr::select(-one_of("max_frame"))

# Filter out videos that are too big or too small
eyeQD_untimed <-
  eyeQD %>%
  filter(is.na(start_frame) | is.na(end_frame)) %>%
  filter(is.na(trial_zoom)) %>%
  arrange(File, Frame) %>%
  group_by(File) %>%
  filter(max_frame < 4000) %>%
  filter(max_frame > 10) %>%
  dplyr::select(-one_of("max_frame"))

# For those videos that do not have time stamps, just give a rough start frame
mean_min <-
  eyeQD_timed %>%
  arrange(File, Frame) %>% 
  group_by(File) %>%
  top_n(-1, Frame) %>%
  dplyr::select(File, Frame) %>%
  ungroup() %>%
  dplyr::summarise(mean_min = mean(Frame))

# Filter out the start frames
eyeQD_untimed <-
  eyeQD_untimed %>%
  mutate(start_frame = mean_min$mean_min) %>%
  filter(Frame > start_frame)

zoomQD <-
  eyeQD %>%
  filter(!is.na(trial_zoom)) %>%
  arrange(File, Frame) %>%
  group_by(File) %>%
  filter(max_frame < 4000) %>%
  filter(max_frame > 10) %>%
  dplyr::select(-one_of("max_frame"))

eyeQD <-
  rbind(as.data.frame(zoomQD), as.data.frame(eyeQD_untimed), as.data.frame(eyeQD_timed)) %>%
  arrange(part_id, File, Frame) %>%
  distinct(.)
```


# Removed videos due to unusual frame rate, maximal frame number <  end frame suggested by Gorilla (To DO: manually check what happened in these videos, and correct start frame and end frame in time_stamp.csv)
```{r}
# List removed trials and reasonings
org_eyeQD %>%
  filter(File %in% c(setdiff(unique(org_eyeQD$File), unique(eyeQD$File)))) %>%
  group_by(part_id, File) %>%
  mutate(max_frame = max(Frame)) %>%
  dplyr::select(part_id, File, frame_rate, max_frame, start_frame, end_frame) %>%
  distinct(.) %>%
  arrange(part_id, File)
```


```{r}
actual_start <-
  eyeQD %>%
  arrange(File, Frame) %>%
  group_by(File) %>%
  filter(row_number()==1) %>%
  dplyr::select(File, Frame) %>%
  dplyr::rename(File= File, actual_start = Frame)

actual_end <-
  eyeQD %>%
  arrange(File, Frame) %>%
  group_by(File) %>%
  filter(row_number()==n()) %>%
  dplyr::select(File, Frame) %>%
  dplyr::rename(File= File, actual_end = Frame)
```


# Print the duplicated or missing frame
```{r}
eyeQD <- merge(eyeQD, actual_start, by.x = "File", by.y = "File", all.x = T)
eyeQD <- merge(eyeQD, actual_end, by.x = "File", by.y = "File", all.x = T)

# Get rid of repeated coding
eyeQD <- eyeQD[-which(duplicated(eyeQD[,c("File", "Frame", "part_id", "block")])),]

eyeQD <- 
  eyeQD %>%
  arrange(part_id, File, Frame)

# Check whether frame numbers match with duration; printed output are videos with extra frame numbers coded
eyeQD$consecutive <- append(NA, diff(eyeQD$Frame))

unique(eyeQD$consecutive)

eyeQD %>%
  filter(consecutive > 1 | consecutive == 0)

skipped <-
  eyeQD %>%
  group_by(File) %>%
  arrange(File, Frame) %>%
  filter(consecutive > 1) %>%
  mutate(duration = actual_end - actual_start + 1,
         diff_start = actual_start - start_frame, 
         diff_end = end_frame - actual_end)

# Print the duplicated or missing frame
codeAgain <-
  eyeQD %>%
  group_by(File) %>%
  mutate(duration = actual_end - actual_start + 1,
         diff_start = actual_start - start_frame, 
         diff_end = end_frame - actual_end) %>%
  filter(consecutive > -5 & consecutive != 1) %>%
  filter(File %in% skipped$File) %>%
  dplyr::select("part_id", "File", "Frame", "consecutive") %>%
  mutate(code_from_frame = Frame - consecutive,
         code_to_frame = Frame - 1) %>%
  dplyr::select(-one_of("Frame", "consecutive")) %>%
  arrange(part_id, File)

head(codeAgain)

# write.csv(codeAgain, "/Volumes/data/projects/smile/recordings/eye_recordings/splash/results/skipped_frame.csv")
```


# Descriptive Stat Summary
```{r}
library(dplyr)

eyeQD %>%
  mutate(part_id = as.factor(part_id)) %>%
  dplyr::count(part_id) %>%
  dplyr::rename(sum = n) %>%
  head()

# Video duration
eyeQD %>%
  mutate(duration = (actual_end - actual_start)/frame_rate) %>%
  group_by(File) %>%
  arrange(File, Frame) %>%
  dplyr::select(File, duration) %>%
  distinct(.) %>%
  head()

unique(eyeQD$part_id)

# write.csv(fbf_id, "/Users/jojohu/Downloads/fbf_id.csv", row.names = F)
```



# Merge Zoom Data with the Social Conditions of the trials
```{r}
condition <- 
  read.csv("/Users/jojohu/Documents/Splash/beh_analysis/results/immRe_data.csv", stringsAsFactors = F)

zoomCoded <- 
  eyeQD %>%
  filter(!is.na(trial_zoom))

unique(zoomCoded$part_id)

zoomBeh <-
  condition %>%
  filter(Participant.Public.ID %in% zoomCoded$part_id) %>%
  arrange(Participant.Public.ID, Spreadsheet.Row) %>%
  dplyr::select(Participant.Public.ID, Spreadsheet.Row, block, social_cond, word_type, story, video_file) %>%
  group_by(Participant.Public.ID, block) %>%
  dplyr::mutate(trial_number_zoom = row_number(),
                trial_zoom = paste0("story"),
                part_id = `Participant.Public.ID`)

zoomIntro <- zoomBeh
zoomIntro$trial_zoom <- "storyintro"
zoomBeh <- rbind(as.data.frame(zoomIntro), as.data.frame(zoomBeh))

zoomCoded <-
  merge(zoomCoded, zoomBeh, by.x = c("part_id", "block_zoom", "trial_zoom", "trial_number_zoom"),
      by.y = c("part_id", "block", "trial_zoom", "trial_number_zoom"), all.x = T)
```


# Merge all non-zoom trials with the Social Conditions of the trials
```{r}
# Read in a file that has identifier of each recording
trialName <- read.csv("/Users/jojohu/Documents/Splash/beh_analysis/results/story_timestamp.csv", stringsAsFactors = F)

trialName$part_id <- str_extract(basename(trialName$new_name), "smile_\\S{1}_\\S{3}")
trialName$trial_number <- str_extract(basename(trialName$new_name), "\\S+(?=.smile)")

trialName <-
  trialName %>%
  filter(part_id %in% eyeQD$part_id) %>%
  distinct(.)

gorillaCoded <-
  eyeQD %>%
  filter(!part_id %in% zoomCoded$part_id)

# Merge the identifier of each recording with the quality codings
gorillaCoded <- merge(gorillaCoded, trialName, all.x = T)

# Now use participant identifier to match behavioral conditions to eye tracking videos 
# Read in a data.frame that contains the behavioral social conditions and the video identifiersfifty_filter
videoCond <- read.csv("/Users/jojohu/Documents/Splash/beh_analysis/results/video_condition.csv")
```


```{r}
gorillaCoded <- 
 merge(gorillaCoded, unique(videoCond[,c("identifier", "Zone.Name", "video_file", "intro_file", "intro_file2", "word_type", "novel_word", "story", "Task.Name", "Spreadsheet.Name")]), by = c("identifier"), all.x = T)

gorillaCoded<-
  gorillaCoded %>%
  filter(`Zone.Name` != "Zone1") %>%
  mutate(social_cond = str_extract(video_file, "(front|side)"),
         trial_type = str_remove(Zone.Name, "file")) %>%
  dplyr::mutate(social_cond = dplyr::recode(social_cond, "front" = "Direct", "side" = "Overhearing")) %>%
  arrange(part_id, as.numeric(trial_number), Frame)

nrow(unique(gorillaCoded[,c("identifier", "Frame")])) == nrow(gorillaCoded)
   
unique(gorillaCoded$trial_type)

zoomCoded <-
  zoomCoded %>%
  mutate(block = block_zoom,
         trial = trial_zoom, 
         trial_number = trial_number_zoom) %>%
  dplyr::select(-one_of("block_zoom", "trial_zoom", "trial_number_zoom"))


gorillaCoded_trim <- 
  gorillaCoded %>%
  dplyr::select(-one_of("block_zoom", "trial_zoom", "trial_number_zoom", "identifier", "Participant.Private.ID", "file_name", "webm", "video_num", "video_subnum",
                        "new_name", "new_path", "copied_path", "STARTED.RECORDING", "STOPPED.RECORDING", "VIDEO.ENDED.EVENT.FIRED", "VIDEO.STARTED", "end_delay", 
                        "recording_duration", "Screen.Number", "Zone.Name", "intro_file", "intro_file2", "Task.Name"))

setdiff(colnames(gorillaCoded_trim), colnames(zoomCoded))

zoomCoded[which(zoomCoded$trial == "story" & zoomCoded$word_type == "noun"), "trial"] <- "videoNoun"  
zoomCoded[which(zoomCoded$trial == "story" & zoomCoded$word_type == "verb"), "trial"] <- "videoVerb" 

zoomCoded[which(zoomCoded$trial == "storyintro" & zoomCoded$word_type == "noun"),"trial"] <- "introNoun"
zoomCoded[which(zoomCoded$trial == "storyintro" & zoomCoded$word_type == "verb"),"trial"] <- "introVerb"
 
unique(zoomCoded$trial)

zoomCoded <-
  zoomCoded %>%
  dplyr::mutate(social_cond = dplyr::recode(social_cond, "front" = "Direct", "side" = "Overhearing"),
                trial_type = trial) %>%
  arrange(part_id, File, Frame)
```


# Missing Frames that need to be coded in Zoom coding
```{r}
zoomCoded %>%
  filter(consecutive != 1) %>%
  filter(consecutive > -1)

# Change proportion > 0.5 to proportion > 0 and remove "good" filtering to save the videoCond data below (TO DO: save the above as a function):
# write.csv(videoCond, "/Users/jojohu/Documents/Splash/beh_analysis/results/eye_quality/video_cond.csv", row.names = F)
```


# Combine Zoom and Gorilla Data
```{r}
allCoded <-
  dplyr::bind_rows(gorillaCoded_trim, zoomCoded) %>%
  filter(str_detect(trial_type, "(videoNoun|videoVerb|introVerb|introNoun)")) %>%
  arrange(part_id, File, Frame) 

coded_part <- unique(allCoded$part_id)

write.csv(coded_part, "/Users/jojohu/Documents/Splash/beh_analysis/results/eye_quality/coded_part.csv", row.names = F)
```


# Mean proportion of trials
```{r}
codeCount_story <- 
  allCoded %>%  
  group_by(part_id, File, trial_type, LookCode) %>%
  dplyr::summarise(n = n())

trialCount_story <- 
  allCoded %>%  
  group_by(part_id, File, trial_type) %>%
  dplyr::summarise(sum = n())


codeCount_story <- merge(codeCount_story, trialCount_story, by = c("part_id", "File", "trial_type"), all.x = T)  

# Trials with more than 10% codable frames
codable_trial <-
  codeCount_story %>% 
  mutate(proportion = n /sum) %>%
  mutate_if(is.numeric, round, 3) %>%
  filter(LookCode == "good" & trial_type != "blockIntro") %>%
  mutate(ten_percent = if_else(proportion > 0.1, 1, 0),
         twenty_percent = if_else(proportion > 0.2, 1, 0),
         fifty_percent = if_else(proportion > 0.5, 1, 0)) %>%
  group_by(part_id) %>%
  dplyr::summarise(total_trial = n(), 
                   ten_percent = sum(ten_percent),
                   twenty_percent = sum(twenty_percent),
                   fifty_percent = sum(fifty_percent)) %>%
  mutate(ten_proportion = ten_percent/total_trial,
         twenty_proportion = twenty_percent/total_trial,
         fifty_proportion = fifty_percent/total_trial) %>%
  mutate_if(is.numeric, round, 2)


write.csv(codeCount_story, "/Users/jojohu/Documents/Splash/beh_analysis/results/eye_quality/trial_quality.csv", row.names = F) 
# Trials with more than 10% codable frames
write.csv(codable_trial, "/Users/jojohu/Documents/Splash/beh_analysis/results/eye_quality/codable_trial.csv", row.names = F) 
```


# Get proportion for each coding criterion
```{r}
goodPro <-
  codeCount_story %>%
  mutate(proportion_good = n/sum) %>%
  distinct(.)

# Label trials that have more than 50% of good trials
fifty_below <-
  codeCount_story %>%
  mutate(proportion = n/sum) %>%
  filter(LookCode == "good") %>%
  filter(proportion < 0.5 | proportion == 0.5)

fifty_above <-
  codeCount_story %>%
  mutate(proportion = n/sum) %>%
  filter(LookCode == "good") %>%
  filter(proportion > 0.5)

# Categorize usable vs. unusable stories
goodPro[which(goodPro$File %in% fifty_below$File), "usage"] <- "unuse"
goodPro[which(goodPro$File %in% fifty_above$File), "usage"] <- "use"

# Merge proportions of coding criteria with by-trial coded data
allPro <- merge(goodPro, allCoded, all.y = T)

id_group <- read.csv("/Users/jojohu/Documents/Splash/beh_analysis/demo/group.csv")

colnames(id_group)[which(colnames(id_group) == "Participant.Public.ID")] <- "part_id"

allPro <- merge(allPro, id_group, all.x = T)
```


# Summarise whether or not participants are usable
```{r}
usage_cond <-
  allPro %>%
  filter(usage == "use") %>%
  dplyr::select(part_id, group, File, trial_type, social_cond, usage) %>%
  distinct(.) %>%
  group_by(part_id, group, trial_type, social_cond, usage) %>%
  dplyr::summarise(n = n()) %>%
  filter(str_detect(trial_type, "video")) %>%
  mutate(trial_type = str_remove(trial_type, ("Noun|Verb"))) %>%
  group_by(part_id, group, trial_type, social_cond, usage) %>%
  dplyr::summarise(n = sum(n)) %>%
  group_by(part_id, group, trial_type) %>%
  dplyr::summarise(usable_condition_count = n()) %>%
  mutate(condition_usage = ifelse(usable_condition_count == 2, "use", "unuse"))
```


# Get count of exclusion reasons for UNusable pasticipants who only has 1 social condition
```{r}
one_cond <- 
  usage_cond %>%
  filter(condition_usage == "unuse") %>%
  distinct(.)

# write.csv(one_cond, "/Users/jojohu/Documents/Splash/beh_analysis/results/eye_quality/unusable_participant_id.csv")

unusable_exclusion <-
  allPro[which(allPro$part_id %in% one_cond$part_id),] %>%
  filter(str_detect(trial_type, "videoNoun|videoVerb")) %>%
  dplyr::select(part_id, group, File, block, LookCode, n, sum, proportion_good) %>%
  distinct(.) %>%
  group_by(part_id, group, block, LookCode) %>%
  dplyr::summarise(n = mean(n), sum = mean(sum), proportion_good = mean(proportion_good)) %>%
  group_by(part_id, group, block) %>%
  dplyr::summarise(exclusion_reason = toString(LookCode)) %>%
  mutate(N = 0.25,
         lighting = ifelse(str_detect(exclusion_reason, "lighting"), 0.25, 0),
         out_of_frame = ifelse(str_detect(exclusion_reason, "out_of_frame"), 0.25, 0),
         blur_movement = ifelse(str_detect(exclusion_reason, "blur_movement"), 0.25, 0),
         blur_camera = ifelse(str_detect(exclusion_reason, "blur_camera"), 0.25, 0),
         distracted_misc = ifelse(str_detect(exclusion_reason, "distracted_misc"), 0.25, 0), 
         child_initiate = ifelse(str_detect(exclusion_reason, "child_initiate"), 0.25, 0),
         sib_interference = ifelse(str_detect(exclusion_reason, "sib_interference"), 0.25, 0),
         parent_interference = ifelse(str_detect(exclusion_reason, "parent_interference"), 0.25, 0)) %>%
  mutate(sum_number_of_reasons = (lighting + out_of_frame + blur_movement + blur_camera + distracted_misc + child_initiate + sib_interference + parent_interference)/0.25) %>%
  mutate(mutiple_reason = ifelse(sum_number_of_reasons == 1, "no", "yes"))
  # dplyr::select(-one_of("block"))

# write.csv(unusable_exclusion, "/Users/jojohu/Documents/Splash/beh_analysis/results/eye_quality/unusable_participant_exclusion.csv")
```


# Get count of exclusion reasons for Usable pasticipants who only has 2 social condition
```{r}
two_cond <- 
  usage_cond %>%
  filter(condition_usage == "use") %>%
  distinct(.)

# write.csv(two_cond, "/Users/jojohu/Documents/Splash/beh_analysis/results/eye_quality/usable_participant_id.csv")

allPro[which(allPro$part_id %in% two_cond$part_id),] %>%
  filter(str_detect(trial_type, "videoNoun|videoVerb")) %>%
  dplyr::select(part_id, group, File, block, LookCode, n, sum, proportion_good) %>%
  distinct(.) %>%
  group_by(part_id, group, block, LookCode) %>%
  dplyr::summarise(n = mean(n), sum = mean(sum), proportion_good = mean(proportion_good)) %>%
  group_by(part_id, group, block) %>%
  dplyr::summarise(exclusion_reason = toString(LookCode)) %>%
  mutate(block_n = 0.25,
         lighting = ifelse(str_detect(exclusion_reason, "lighting"), 0.25, 0),
         out_of_frame = ifelse(str_detect(exclusion_reason, "out_of_frame"), 0.25, 0),
         blur_movement = ifelse(str_detect(exclusion_reason, "blur_movement"), 0.25, 0),
         blur_camera = ifelse(str_detect(exclusion_reason, "blur_camera"), 0.25, 0),
         distracted_misc = ifelse(str_detect(exclusion_reason, "distracted_misc"), 0.25, 0), 
         child_initiate = ifelse(str_detect(exclusion_reason, "child_initiate"), 0.25, 0),
         sib_interference = ifelse(str_detect(exclusion_reason, "sib_interference"), 0.25, 0),
         parent_interference = ifelse(str_detect(exclusion_reason, "parent_interference"), 0.25, 0)) %>%
  mutate(sum_number_of_reasons = (lighting + out_of_frame + blur_movement + blur_camera + distracted_misc + child_initiate + sib_interference + parent_interference)/0.25) %>%
  mutate(mutiple_reason = ifelse(sum_number_of_reasons == 1, "no", "yes"))
  # dplyr::select(-one_of("block"))

track_loss <-
  allPro[which(allPro$part_id %in% two_cond$part_id),] %>%
  filter(str_detect(trial_type, "videoNoun|videoVerb")) %>%
  dplyr::select(part_id, group, File, block, LookCode, n, sum, proportion_good) %>%
  distinct(.) %>%
  group_by(part_id, group, block, LookCode) %>%
  filter(LookCode == "good") %>%
  filter(proportion_good < 0.5) %>%
  group_by(part_id, block) %>%
  dplyr::summarise(track_loss = n())

totalStory <-
  allPro[which(allPro$part_id %in% two_cond$part_id),] %>%
  filter(str_detect(trial_type, "videoNoun|videoVerb")) %>%
  dplyr::select(part_id, group, block, File) %>%
  distinct(.) %>%
  group_by(part_id, group, block) %>%
  dplyr::summarise(total = n())

track_loss <- merge(totalStory, track_loss, all.x = T)

track_loss %>%
  filter(group == "ASD") %>%
  mutate(track_loss = ifelse(is.na(track_loss), 0, track_loss)) %>%
  mutate(trial_loss = track_loss/total) %>%
  dplyr::summarise(mean = mean(trial_loss, na.rm = T), sd = sd(trial_loss, na.rm = T))

track_loss %>%
  filter(group == "TD") %>%
  mutate(track_loss = ifelse(is.na(track_loss), 0, track_loss)) %>%
  mutate(trial_loss = track_loss/total) %>%
  dplyr::summarise(mean = mean(trial_loss, na.rm = T), sd = sd(trial_loss, na.rm = T))

track_loss <- 
  track_loss %>%
  mutate(usage = ifelse(track_loss == total, "loss", "kept"),
         N = 0.25)

track_loss %>%
  group_by(group, usage) %>%
  filter(group == "ASD") %>%
  dplyr::summarise(n = sum(N)) %>%
  mutate(loss_percent = n/sum(n))


track_loss %>%
  group_by(group, usage) %>%
  filter(group == "TD") %>%
  dplyr::summarise(n = sum(N)) %>%
  mutate(loss_percent = n/sum(n))

write.csv(track_loss, "/Users/jojohu/Documents/Splash/beh_analysis/results/eye_quality/usable_participant_trackloss.csv", row.names = F)
```


# Save thefile names of video that are usable for directional coding
```{r}
badVideo <-
  allPro[which(allPro$part_id %in% two_cond$part_id),] %>%
  dplyr::select(part_id, group, File, block, LookCode, n, sum, proportion_good) %>%
  distinct(.) %>%
  group_by(part_id, group, File, LookCode) %>%
  filter(LookCode == "good") %>%
  filter(proportion_good < 0.5) %>%
  mutate(current_path = paste0("/Volumes/data/projects/smile/recordings/eye_recordings/splash/", part_id, "/", "block", block, "/", File, ".mp4"),
         bad_data_path = paste0("/Volumes/data/projects/smile/recordings/eye_recordings/splash/", part_id, "/", "bad_data/", File, ".mp4"),
         current_webm_path = paste0("/Volumes/data/projects/smile/recordings/eye_recordings/splash/", part_id, "/", "block", block, "/", File, ".webm"),
         bad_webm_path = paste0("/Volumes/data/projects/smile/recordings/eye_recordings/splash/", part_id, "/", "bad_data/", File, ".webm"))

lapply(unique(file.path("/Volumes/data/projects/smile/recordings/eye_recordings/splash", badVideo$part_id, "bad_data")),
       function(x) if(!dir.exists(x)) dir.create(x))

file.rename(badVideo$current_path, badVideo$bad_data_path)
file.rename(badVideo$current_webm_path, badVideo$bad_webm_path)
```


# Get count of participants who have been gnerally coded block-by-block
```{r}
blockCodingTD <- read.csv("/Volumes/data/projects/smile/recordings/eye_recordings/splash/results/Data Quality Master Spreadsheet  - TD.csv", stringsAsFactors = F)
blockCodingASD <- read.csv("/Volumes/data/projects/smile/recordings/eye_recordings/splash/results/Data Quality Master Spreadsheet  - ASD.csv", stringsAsFactors = F)

blockCodingTD <-
  blockCodingTD %>%
  mutate(part_id = SID, nonideal_study_space = Non.ideal.study.space..e.g...child.on.bed..non.stable.laptop.) %>%
  dplyr::select(-one_of("SID", "X", "X.1", "X.2"))
  
blockCodingASD <-
  blockCodingASD %>%
  mutate(part_id = X, nonideal_study_space = Non.ideal.study.space) %>%
  dplyr::select(-one_of("X"))

commonCol <- intersect(colnames(blockCodingTD), colnames(blockCodingASD))

blockCodingTD[commonCol] <- sapply(blockCodingTD[commonCol], as.character)
blockCodingASD[commonCol] <- sapply(blockCodingASD[commonCol], as.character)

blockCoding <- 
  dplyr::bind_rows(blockCodingTD, blockCodingASD) %>%
  dplyr::select(commonCol) %>%
  dplyr::rename(block_number = Block.Number, tech_issue_not_start = Tech.issues.before.experiment...did.not.start.experiment, tech_issue_not_complete = Tech.issues.during.experiment...can.t.complete.experiment,
                webcam_off = Webcam.did.not.capture.children.s.eyes.at.all..due.to.only.capturing.experimenter.or.webcam.camera.off., home_too_loud = Home.Environment.too.Loud)

blockCoding[,c("block_number", "tech_issue_not_start", "tech_issue_not_complete", "webcam_off", "home_too_loud")] <-
  sapply(blockCoding[,c("block_number", "tech_issue_not_start", "tech_issue_not_complete", "webcam_off", "home_too_loud")], as.numeric)

blockCoding <- merge(blockCoding, id_group, all.x = T)

generalCoding <-
  blockCoding %>%
  dplyr::select("part_id", "group", "Source", "block_number", "tech_issue_not_start", "tech_issue_not_complete", "webcam_off", "home_too_loud", "nonideal_study_space") %>%
  distinct(.) %>%
  mutate(N = 0.25,
         block = block_number,
         frame_coding_usage = ifelse(part_id %in% unusable_exclusion$part_id, "unuse", "unknown")) %>%
  mutate(tech_issue_not_start = ifelse(tech_issue_not_start == 1, 0.25, 0),
         tech_issue_not_complete = ifelse(tech_issue_not_complete == 1, 0.25, 0),
         webcam_off = ifelse(webcam_off == 1, 0.25, 0),
         home_too_loud = ifelse(home_too_loud == 1, 0.25, 0),
         nonideal_study_space = ifelse(nonideal_study_space == 1, 0.25, 0)) %>%
  dplyr::select(-one_of("block_number", "Source"))
    
generalCoding[which(generalCoding$part_id %in% track_loss$part_id), "frame_coding_usage"]  <- "use"

allFBF <-
  allPro %>%
  filter(str_detect(trial_type, "videoNoun|videoVerb")) %>%
  dplyr::select(part_id, group, File, block, LookCode, n, sum, proportion_good) %>%
  distinct(.) %>%
  group_by(part_id, group, block, LookCode) %>%
  dplyr::summarise(n = mean(n), sum = mean(sum), proportion_good = mean(proportion_good)) %>%
  group_by(part_id, group, block) %>%
  dplyr::summarise(exclusion_reason = toString(LookCode)) %>%
  mutate(block_n = 0.25,
         lighting = ifelse(str_detect(exclusion_reason, "lighting"), 0.25, 0),
         out_of_frame = ifelse(str_detect(exclusion_reason, "out_of_frame"), 0.25, 0),
         blur_movement = ifelse(str_detect(exclusion_reason, "blur_movement"), 0.25, 0),
         blur_camera = ifelse(str_detect(exclusion_reason, "blur_camera"), 0.25, 0),
         distracted_misc = ifelse(str_detect(exclusion_reason, "distracted_misc"), 0.25, 0), 
         child_initiate = ifelse(str_detect(exclusion_reason, "child_initiate"), 0.25, 0),
         sib_interference = ifelse(str_detect(exclusion_reason, "sib_interference"), 0.25, 0),
         parent_interference = ifelse(str_detect(exclusion_reason, "parent_interference"), 0.25, 0)) 
```
 


# Merge general coding with Frame-by-frame coding
```{r}
allCoding <- merge(generalCoding, allFBF, by = c("part_id", "block", "group"), all = T) 

allCoding <-
  allCoding %>%
  dplyr::select(-one_of("webcam_off")) %>%
  mutate_if(is.numeric , replace_na, replace = 0) %>%
  mutate(block_usage1 =  ifelse((tech_issue_not_start|tech_issue_not_complete|home_too_loud|nonideal_study_space == 0.25) & (frame_coding_usage == "unknown"), "unuse", NA)) %>%
  mutate(block_usage2 =  ifelse(tech_issue_not_start == 0 & tech_issue_not_complete == 0 & home_too_loud == 0 & nonideal_study_space == 0 & frame_coding_usage == "unknown", "use", NA)) %>%
  mutate(block_usage = coalesce(block_usage1, block_usage2))

allCoding[which(allCoding$frame_coding_usage == "unknown"), "frame_coding_usage"] <- NA

which(duplicated(allCoding[,c("part_id", "block")]))

allCoding <-
  allCoding %>%
  mutate(usage = coalesce(frame_coding_usage, block_usage)) %>%
  # filter(!is.na(usage)) %>%
  dplyr::rowwise() %>%
  dplyr::mutate(sum_number_of_reasons = sum(tech_issue_not_start, tech_issue_not_complete, home_too_loud, nonideal_study_space, lighting, out_of_frame, blur_movement, blur_camera, distracted_misc, child_initiate, sib_interference, parent_interference, na.rm = T)) %>%
  dplyr::mutate(sum_number_of_reasons = sum_number_of_reasons/0.25)  %>%
  dplyr::mutate(mutiple_reason = ifelse(sum_number_of_reasons > 1, 0.25, 0)) %>%
  dplyr::select(-one_of("block", "exclusion_reason", "frame_coding_usage", "block_usage", "block_n", "block_usage1", "block_usage2")) %>%
  dplyr::relocate(N, .after = part_id)

allCoding %>%
  filter(is.na(group))

allCoding[which(allCoding$part_id == "smile_c_011" | allCoding$part_id == "smile_c_021"), "group"] <- "TD" 
allCoding[which(allCoding$part_id == "smile_c_205"), "group"] <- "ASD" 

allCoding %>%
  dplyr::select(part_id, group) %>%
  distinct(.) %>%
  group_by(group) %>%
  dplyr::summarise(n = n())
  

sumCategory <- 
  allCoding %>% 
  group_by(usage, group) %>% 
  dplyr::summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE))) %>%
  dplyr::select(-one_of("sum_number_of_reasons"))

write.csv(allCoding, "/Users/jojohu/Documents/Splash/beh_analysis/results/eye_quality/general_coding_summary.csv", row.names = F)
write.csv(sumCategory, "/Users/jojohu/Documents/Splash/beh_analysis/results/eye_quality/sum_category.csv", row.names = F)
```



